|

### 2020-06-16 appendix/appendix_final.Rmd
minor fixes

# Search criteria

The first step in reviews is to gather a sample of records. This initial procedure is the foundation for the entire meta-analytical process: if the goal is to aggregate all the available data on a given topic, the primary pool must contain all of it. At the same time, the sample should be concise enough to optimise the work flow. Upon selecting the online databases, we attempted to do a "term" search, based on a set of words we scouted from the distributive politics literature we already knew. This search produced oversized databases, of which a large share was completely unrelated to our subject of investigation. The strategy we found to be the most thorough and productive was to select the records that cited Weingast, Shepsle and Johnsen's 1981 paper "The political economy of benefits and costs: A neoclassical approach to distributive politics". Although \href{https://scholar.google.com/}{Google Scholar} reports the article amounts to \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations\footnote{As of May 11\textsuperscript{th}, 2020.}, as of the 21\textsuperscript{st} of November 2019, our search resulted in a total of 2,664 records.

@@

The selection process was conducted by two authors in three phases. In the first round, we excluded all titles that were obviously unrelated to our topic of investigation. For instance, we curiously found articles about automobile motors amidst our sample. We consider this a preliminary step, since we were not able to eliminate a large number of entries. Thus, we read all abstracts. We chose to maintain those that indicated either government expenditure or legislative structures were central matters. For instance, if the paper sought to identify variables that increased government size, it was maintained. Abstracts that indicated the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics, for example, were also included. This allowed us to significantly reduce our sample to 376 records.

@@

## Exclusion analysis

@@

# Meta-analysis dataset

The meta-analytic data is comprised of two datasets. The first dataset has the main coefficients that were reported in the paper. It includes only the most rigorous model from each paper, that is, those estimated with the largest $n$, most control variables, and fixed effects if the authors added them. If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one. This sample encompasses 36 estimates, as 10 articles analysed two dependent or independent variables of interest. Our second sample, in contrast, contains all the 126 effect sizes reported in the 26 papers.

In the main text, we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set. Below is the data extraction process for all relevant coefficients in the selected articles. In the \@ref(meta-an) and \@ref(meta-reg) sections of this Appendix, you will find all tests performed in both reduced and full samples.

# Descriptive statistics

@@

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
dat %>%
  select(id, published) %>%
  unique() %>%
  ggplot(aes(x = as.factor(published))) + 
    geom_bar(color = "black") + 
  labs(x = "Published study?",
       y = "") + 
  theme_bw()
```

## Electoral system

There are many differences in the papers relative to the research design. One remarkable difference is the application of the theory, that was build with majoritarian systems in mind, in non-majoritarian democracies. In our sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that the argument for working in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographycally concentrated. The concentration facilitates politicians to use pork-barrel project to captivate their electoral supporters.}

@@

## Dependent variables

@@

## Independent variables

@@

This test has at least two advantages. First, it is robust to the design of the paper. As papers select different types of journals, countries, samples, and other characteristics, this increases the heterogeneity. This test ignores the design discrepancies and focus on the overall effect. Second, this test has the advantage of be simple and straightfoward. It requires very few assumption and has a direct statistical formulation. The disadvantage is that we can extract more information with meta-regressions.

@@

# Meta-analysis {#meta-an}

@@

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

@@

### Electoral system subgroup analysis

@@

@@

@@

@@

# Meta-Analysis (all coefficients) {#full-meta-an}

@@

```{r, echo=FALSE, fig.width=12, fig.height=6, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
build_forest(mod, NULL)
```

@@

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### Electoral system subgroup analysis

@@

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

# Meta-regressions {#meta-reg}

## Meta-regressions for Expenditure as a Percentage of the GDP

@@

@@

1. Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
2. Year has a positive effect: the younger the publication, the higher the detected coefficient.
3. Unpublished papers tend to have higher coefficients than published papers.
4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.

## Meta-regressions for Expenditure Per Capita

@@

With all coefficients, the results of the effect sizes on the Expenditure Per Capita Regressions are the following:

1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
2. Year has now a positive effect on coefficient sizes.
3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the effects on per capita expenditure found in our models.
4. In terms of the modeling, passing from `OLS` to `PANEL` decreases the detected effects.
5. All other coeffients were not significant.

@@

1. Unpublished papers report a significantly higher coefficient.
2. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
3. All other coefficients remained insignificant.

@@

# The Theory behind the Meta Analysis

@@

These sources of heterogeneity have two implications. First, it makes our estimates very disperse. The heterogeneity tests are all but one significant. When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates. Second, the amount of heterogeneity makes fixed effects estimates unrealistic and bised. Thus, we opt for random effects model.

Let each study having an effect of $T_i$. In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ come from, $\theta_i$, and a within-study error $\varepsilon_i$:

@@

# Robustness: Full model meta-regressions combined {#full-meta-reg}

@@

1. The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP)
2. The type of the independent variable in the stydy (N, K, log of N);
3. The electoral system (Majoritarian, Proportional Representation, and Mixed).

@@

# Auxiliary functions

## Function for generate the Meta-Analytic Figures

This function receives the meta-analysis results and build a forest plot using `ggplot2`.

@@

## Webscraping code

>>>>

# Search Criteria

The first step in reviews is to gather a sample of records. This initial procedure is the foundation for the entire meta-analytical process: if the goal is to aggregate all the available data on a given topic, the primary pool must encompass all of it. At the same time, the sample should be concise enough to optimise the work flow. Upon selecting the online databases, we attempted to do a "term" search, based on a set of words we scouted from the distributive politics literature we already knew. This search produced oversized databases, of which a large share was completely unrelated to our subject of investigation. The strategy we found to be the most thorough and productive was to select the records that cited Weingast, Shepsle and Johnsen's 1981 paper "The political economy of benefits and costs: A neoclassical approach to distributive politics". Although \href{https://scholar.google.com/}{Google Scholar} reports the article amounts to \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations\footnote{As of May 11\textsuperscript{th}, 2020.}, as of the 21\textsuperscript{st} of November 2019, our search resulted in a total of 2,664 records.

@@

The selection process was conducted by two authors in three phases. In the first round, we excluded all titles that were obviously unrelated to our topic. For instance, we curiously found articles about automobile motors amidst our sample. We consider this a preliminary step, since we were not able to eliminate a large number of entries. Thus, we read all abstracts. We chose to maintain those that indicated either government expenditure or legislative structures were central matters. For instance, if the paper sought to identify variables that increased government size, it was maintained. Abstracts that indicated the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics, for example, were also included. This allowed us to significantly reduce our sample to 376 records.

@@

## Exclusion Analysis

@@

# Meta-Analysis Dataset

The meta-analytic data is comprised of two datasets. The first has the main coefficients that were reported in the paper. It includes only the most rigorous model from each paper, that is, those estimated with the largest $n$, most control variables, and fixed effects if the authors added them. If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one. This sample encompasses 36 estimates, as 10 articles analysed two dependent or independent variables of interest. Our second sample, in contrast, contains all the 126 effect sizes reported in the 26 papers.

In the main text, we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set. Below is the data extraction process for all relevant coefficients in the selected articles. In the Meta-Analysis and Meta-Regressions sections of this Appendix, you will find all tests performed in both reduced and full samples.

# Descriptive Statistics

@@

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
dat %>%
  select(id, published) %>%
  unique() %>%
  ggplot(aes(x = as.factor(published))) + 
    geom_bar(color = "black") + 
  labs(x = "Published Study?",
       y = "") + 
  theme_bw()
```

## Electoral System

There are many differences in the papers relative to the research design. One remarkable difference is the application of the theory, that was build with majoritarian systems in mind, to non-majoritarian democracies. In our sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that the argument for working in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographycally concentrated. The concentration facilitates politicians to use pork-barrel project to captivate their electoral supporters.}

@@

## Dependent Variables

@@

## Independent Variables

@@

This test has two advantages. First, it is robust to the design of the paper. As papers select different types of journals, countries, samples, and other characteristics, this increases the heterogeneity. This test ignores the design discrepancies and focus on the overall effect. Second, this test has the advantage of be simple and straightfoward. It requires very few assumption and has a direct statistical formulation. The disadvantage is that we can extract more information with meta-regressions.

@@

# Meta-Analysis

@@

1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

@@

### Electoral System Subgroup Analysis

@@

Now, we look into the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).

@@

1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

@@

This model investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.

@@

# Meta-Analysis (All Coefficients)

@@

```{r, echo=FALSE, fig.width=12, fig.height=6, fig.cap="Effect of Lower House Size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
build_forest(mod, NULL)
```

@@

1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### Electoral System Subgroup Analysis

@@

1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

# Meta-Regressions

## Meta-Regressions for Expenditure as a Percentage of the GDP

@@

We have the following results for the meta-regressions of Expenditure as a Percentage of GDP:

@@

1. Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
2. Year has a positive effect: the younger the publication, the higher the detected coefficient.
3. Unpublished papers tend to have higher coefficients than published papers.
4. Passing from `Majoritarian` to `Non-Majoritarian` significantly decreases the effects found in our models.
5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
6. Passing from `Local` to `State` or `World` levels decreases the detected effect size.

## Meta-Regressions for Expenditure Per Capita

@@

With all coefficients, the results of the effect sizes on the Expenditure Per Capita regressions are the following:

1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
2. Year has now a positive effect on coefficient sizes.
3. Passing electoral rules from `Majoritarian` to `Non-Majoritarian` significantly increases the effects on per capita expenditure found in our models.
4. In terms of the modeling, passing from `OLS` to `PANEL` decreases the detected effects.
5. All other coeffients were not significant.

@@

1. Unpublished papers report significantly higher coefficients.
2. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
3. All other coefficients remained insignificant.

@@

# The Theory Behind the Meta Analysis

@@

These sources of heterogeneity have two implications. First, they make our estimates very disperse. All but one of our heterogeneity tests are significant. When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates. Second, the amount of heterogeneity makes fixed effects estimates unrealistic and biased. Thus, we opt for random effects model.

Let each study having an effect of $T_i$. In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ comes from, $\theta_i$, and a within-study error $\varepsilon_i$:

@@

# Robustness: Full model Meta-Regressions Combined

@@

1. The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP)
2. The type of the independent variable in the stydy ($N$, $K$, $log (N)$);
3. The electoral system (Majoritarian, Proportional Representation, and Mixed).

@@

# Auxiliary Functions

## Function to Generate Meta-Analytic Figures

This function receives the meta-analysis results and builds a forest plot using `ggplot2`.

@@

## Webscraping Code
